---
title: "Whole Game"
output: html_notebook
---

```{r setup}
library(tidyverse)
```

##Data import
```{r}
permit_raws <- read_csv("dataPermit_full.csv", na = "null")
permit_raws
```

* area = metropolitan standar area
* date = month/year (character vector or strings)
* f1 = 1 family house, f24  = 2-4 families, f5 = 5+ family house
* units = number of buidings, change in units; value = average value of building; valchange = change in value


```{r}
permits <- permit_raws %>% 
  separate(date, c("month", "year"), "/", convert = TRUE) %>% 
  filter(year > 2007) %>% 
  select(-ends_with("change"))
permits
```


## Basic EDA

```{r}
permits %>% count(year)
permits %>% count(area)
permits %>% count(area) %>% count(n)
```

I'm focus on sigle family home

```{r}
permits <- permits %>% 
  mutate(date = year + (month - 1) / 12 )

ggplot(permits, aes(date, f1units)) +
  geom_line(aes (group = area))
```


## Focus

Focus on big cities. Maybe bias our data because big cities are different from small cities?

```{r}
f1units <- permits %>%
  group_by(area) %>% 
  summarise(mean = mean(f1units)) %>% 
  arrange(desc(mean))
f1units

f1units %>% filter(mean > 100)

permits_big <- permits %>% 
  semi_join(f1units %>% filter(mean > 100))
permits_big
```

```{r}
ggplot(permits_big, aes(date, f1units)) +
  geom_line(aes(group = area))

ggplot(permits_big, aes(date, f1units)) +
  geom_line(aes(group = area), alpha = 1/10)

ggplot(permits_big, aes(date, f1units)) +
  geom_line(aes(group = area), alpha = 1/10) +
  scale_y_log10() +
  geom_smooth(se = FALSE)

```

## Model



